Applying Renormalization Group Theory to the Square Well Liquid

### 2014-06-16 papers/thesis-roth/project.tex

\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{figs/coexistance_SW}
  \end{center}
  \caption{Liquid-vapor coexistence for a square well liquid.}
  \label{fig:coexistance_SW}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{figs/coexistence-RG-forte}
  \end{center}
  \caption{Liquid-vapor coexistence, compared with Forte's 2011 data}
  \label{fig:coexistence-RG-forte}
\end{figure}

Figures~\ref{fig:phi-RG-lowT} and~\ref{fig:phi-RG-highT} show the
grand free energy per unit volume at a low temperature and near the
critical point, respectively, for a value of $\lambdaSW = 1.5$. Results are not particularly clear at
this point, as the program has not been fully debugged. This is
evident in figure~\ref{fig:phi-RG-lowT}; one notes that the curve for
$i=1$ is neither complete nor
accurate. Figure~\ref{fig:coexistence-RG-forte} gives an even starker
picture of the shortcomings of my RG implementation. We see that the
baseline ($i=0$; identical to SW calculations) is reasonable, with
expected shortcomings near the critical point. However, calculations
including even one iteration ($i=1$) flat-out fail.

>>>>

\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{figs/coexistence_SW}
  \end{center}
  \caption{Liquid-vapor coexistence for a square well liquid.}
  \label{fig:coexistance_SW}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{figs/coexistence-RG-forte}
  \end{center}
  \caption{Liquid-vapor coexistence, compared with Forte's 2011 data, and with molcular dynamics simulations from White\cite{White00}}
  \label{fig:coexistence-RG-forte}
\end{figure}

Figures~\ref{fig:phi-RG-lowT} and~\ref{fig:phi-RG-highT} show the
grand free energy per unit volume at a low temperature and near the
critical point, respectively, for a value of $\lambdaSW = 1.5$. Results are not particularly clear at
this point, as the program has not been fully debugged. This is
evident in figure~\ref{fig:phi-RG-lowT}; one notes that the curve for
$i=1$ is neither complete nor
accurate. Figure~\ref{fig:coexistence-RG-forte} gives another
picture of the shortcomings of my RG implementation. We see that the
baseline ($i=0$; identical to SW calculations) is reasonable, with
expected shortcomings near the critical point. However, calculations
including even one iteration ($i=1$) are not included because they flat-out fail.
